What We Eval in the Shadows

### 2021-04-15 paper/main.tex
Update Kaggle

\subsection{Kaggle}
Only \kaggleNbruns scripts trigger \eval. In total, \kaggleAllcalls \eval were
recorded; none are calls to variants. Out of \kaggleStaticeval call sites,
\kaggleTriggeredeval were exercised. Most call sites are invoked only once. Only
one site is called \kaggleMaxcalls times. Expressions amount for
\kaggleCodepercent of arguments. Unlike CRAN corpus, there are very few symbols
(\kaggleSymbolpercent). Most expressions result from calls to \c{parse}, thus
most \evals start with strings. The median argument size is \kaggleMedianszeval,
which makes sense, as few arguments are only symbols. The largest argument is
\kaggleMaxszeval. The distribution of instructions per eval is similar to CRAN;
\kaggleSmalleventspct of \evals execute fewer than 50 instructions. Manual
inspection of \eval usage in Kaggle suggest that it is consistent with the data
obtained for CRAN. We do not discuss it further.

>>>>

\subsection{Kaggle}

In total, \kaggleAllcalls \eval were recorded, all to \eval function. Out of
\kaggleStaticeval sites from \KaggleWithEvals, only \kaggleTriggeredeval sites
in \kaggleNbruns scripts were hit. \KaggleFailedScripts scripts failed to run
and the other did not exercised the \eval sites. This is partially expected
as Kaggle code does not need to abide to any checks. Upon a manual inspection,
we observed that indeed the failing scripts were of a poor quality, often not
finished, using misspelled package names, hard-coded file paths or accessing
missing files.

Most call sites are invoked only once. Only one site is called \kaggleMaxcalls times.
Expressions amount for \kaggleCodepercent of arguments. Unlike CRAN corpus,
there are very few symbols (\kaggleSymbolpercent). Most expressions result from
calls to \c{parse}, thus most \evals start with strings. The median argument
size is \kaggleMedianszeval, which makes sense, as few arguments are only
symbols. The largest argument is \kaggleMaxszeval. The distribution of
instructions per eval is similar to CRAN; \kaggleSmalleventspct of \evals
execute fewer than 50 instructions. Manual inspection of \eval usage in Kaggle
suggest that it is consistent with the data obtained for CRAN. We do not
discuss it further.
